A quantitative framework for investigating the reliability of empirical network construction: supplemental information

### 2018-06-27 manuscript/supplemental.tex
Tomas comments to supplemental

@@

      The \emph{Salix}-galler-parasitoid meta-network dataset collected 
      by~\citet{Kopelke2017} consists of a single community type sampled across 
      Europe: willow (\emph{Salix}) species, willow-galling sawflies (Hymenoptera, Tenthredinidae, Nematinae, Euurina), and their natural 
      enemies (hymenopteran parasitoids and coleopteran, lepidopteran, dipteran, 
      and hymenopteran inquilines). The data were collected over 29 years 
      (1982-2010) at 374 unique locations across Europe ranging from Sicily to 
      the Arctic. Including repeated visits to a number of sites, the data set 
      contains 641 site-visits. Here we take the more conservative approach and pool visits to the same site for a sample size of 374 sub-networks.

@@

      As with the galler-natural enemy component, we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species (\emph{Appendix S6}). We obtained prior parameters of $\alpha$=8.72, $\beta$=305 for the \emph{Salix}-galler component. These prior parameters were then used to estimate the posterior distribution.

@@

      \begin{figure}[h!]
        \caption{Using prior distributions based on the \emph{Salix}-galler network sampled at a single site in~\citet{Kopelke2017}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting. Here we show posterior distributions for $\lambda$ ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times. The distribution narrows and approaches zero as the sample size increases. Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top of each panel) approaches zero and the 95\% credible interval (lines at top of each panel) narrows as sample size increases. Dashed lines indicate threshold probabilities of 0.1, 0.05, and 0.01.}
        \label{Salix_pdfs}
        \begin{center}
        \includegraphics*[width=.7\textwidth]{figures/SG_pdfs_increasing_N_Zillis.eps}
        \end{center}
        \end{figure}

>>>>

    To create Bayesian distributions for the probability of interactions, we must begin with a prior distribution. This distribution reflects our prior knowledge (or lack thereof) about the likelihood of a given interaction. Priors may be selected to be uninformative, so as not to bias the posterior distribution in any particular direction, or may be informative and based on some prior knowledge about the system.

@@

      The \emph{Salix}-galler-parasitoid meta-network dataset collected 
      by~\citet{Kopelke2017} consists of a single community type sampled across 
      Europe: willow (\emph{Salix}) species, willow-galling sawflies (Hymenoptera, Tenthredinidae, Nematinae, Euurina), and their natural 
      enemies (hymenopteran parasitoids and coleopteran, lepidopteran, dipteran, 
      and hymenopteran inquilines). The data were collected over 29 years 
      (1982-2010) at 374 unique locations across Europe ranging from Sicily to 
      the Arctic. Since the dataset includes repeated visits to a number of sites, the data set 
      contains 641 site-visits. Here we take the more conservative approach and pool visits to the same site for a sample size of 374 sub-networks.

@@

      As with the galler-natural enemy component (presented in the main text), we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species (\emph{Appendix S6}). We obtained prior parameters of $\alpha$=8.72, $\beta$=305 for the \emph{Salix}-galler component. These prior parameters were then used to estimate the posterior distribution.

@@

      \begin{figure}[h!]
        \caption{Using prior distributions based on the \emph{Salix}-galler network sampled at a single site in~\citet{Kopelke2017}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting. Here we show posterior distributions for $\lambda$ ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times. The distribution narrows and approaches zero as the sample size increases. Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top) approaches zero and the 95\% credible interval (lines at top) narrows as sample size increases. Dashed lines indicate threshold probabilities of 0.1, 0.05, and 0.01.}
        \label{Salix_pdfs}
        \begin{center}
        \includegraphics*[width=.7\textwidth]{figures/SG_pdfs_increasing_N_Zillis.eps}
        \end{center}
        \end{figure}
